Discussion Draft

### 2020-04-13 doc/Discussion.rmd
rough draft of caveats for typical landscape

# consequences of conserved typical landscape
# (sardel kirkptarick - the rec landscape -- diviation from uniform is due to male rec landscape
# (female CO suppresion -- DSB (repaired as NCO -- elevated DsB (halldorsson?))  )
#

>>>>

# consequences of conserved typical landscape
# most exceptions to the typical landscape, marsupials (pig and tomoato)

#(sardel kirkptarick -

# diviation from uniform is due to male rec landscape
# patterns of Fst (Hanel et al, but see Kartej?)
# source could be DSB formation along chromosome - and /or biases in DSB repair 
#CO suppresion, elevated DSB (most repaired as NCO) -- elevated DsB (Brick))  )
#
